**The status of the microbial census: an update**

### 2016-02-02 results/tables/build_archaeal_category_phylum_table.Rmd
Rerun entire makefile with updated metadata files
Fix row labels in supplemental figures

data <- read.table(file="data/process/phylum_category_counts.tsv", header=T)

archaea <- data[data$domain=="archaea",-1]
archaea <- archaea[order(archaea$total, decreasing=T), names(categories)]
colnames(archaea) <- gsub("total", "Total", colnames(archaea))
rownames(archaea) <- gsub("Candidate_division_", "", rownames(archaea))
rownames(archaea) <- gsub("_", " ", rownames(archaea))

@@

caption <- "\\textbf{Supplementary Table 3. Frequency that each archaeal phylum was found across each of the environmental categories.}"

>>>>

data <- read.table(file="data/process/phylum_category_counts.tsv", header=T)
archaea <- data[data$domain=="archaea",]
rownames(archaea) <- archaea$phylum
archaea <- archaea[,-c(1,2)]

archaea <- archaea[order(archaea$total, decreasing=T), names(categories)]
colnames(archaea) <- gsub("total", "Total", colnames(archaea))
rownames(archaea) <- gsub("Candidate_division_", "", rownames(archaea))
rownames(archaea) <- gsub("_", " ", rownames(archaea))

@@

caption <- "\\textbf{Supplementary Table 5. Frequency that each archaeal phylum was found across each of the environmental categories.}"

### 2016-02-02 results/tables/build_bacterial_category_phylum_table.Rmd
Rerun entire makefile with updated metadata files
Fix row labels in supplemental figures

data <- read.table(file="data/process/phylum_category_counts.tsv", header=T)

bacteria <- data[data$domain=="bacteria",-1]
bacteria <- bacteria[order(bacteria$total, decreasing=T), names(categories)]
colnames(bacteria) <- gsub("total", "Total", colnames(bacteria))
rownames(bacteria) <- gsub("Candidate_division_", "", rownames(bacteria))
rownames(bacteria) <- gsub("_", " ", rownames(bacteria))

@@

caption <- "\\textbf{Supplementary Table 2. Frequency that each bacterial phylum was found across each of the environmental categories.}"

>>>>

data <- read.table(file="data/process/phylum_category_counts.tsv", header=T)
bacteria <- data[data$domain=="bacteria",]
rownames(bacteria) <- bacteria$phylum
bacteria <- bacteria[,-c(1,2)]

bacteria <- bacteria[order(bacteria$total, decreasing=T), names(categories)]
colnames(bacteria) <- gsub("total", "Total", colnames(bacteria))
rownames(bacteria) <- gsub("Candidate_division_", "", rownames(bacteria))
rownames(bacteria) <- gsub("_", " ", rownames(bacteria))

@@

caption <- "\\textbf{Supplementary Table 4. Frequency that each bacterial phylum was found across each of the environmental categories.}"
